---
title: "Waypoint and map for SE2204 cruise"
author: "Johanna Wren"
date: "April 29, 2022"
output:
  html_document:
    toc: yes
    df_print: paged
  html_notebook:
    code_folding: hide
    theme: flatly
    toc: yes
    toc_float:
      collapsed: no
      tod_depth: 3
---

<script>
$(document).ready(function() {
  $items = $('div#TOC li');
  $items.each(function(idx) {
    num_ul = $(this).parentsUntil('#TOC').length;
    $(this).css({'text-indent': num_ul * 10, 'padding-left': 0});
  });

});
</script>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = '~/Documents/Cruises/BEToceanography/SE2204 - Hot Spot/')
```

# Description
This script calculates waypoints along the cruise track based on ship speed and sampling duration at various locations. 

Outputs are a simple map with waypoints and a table with the timing at each waypoint. 

# Prepare workspace
```{r message=FALSE}
# Clear workspace
rm(list=ls())

# Set working directory
mainDir <- '~/Documents/Cruises/BEToceanography/SE2204 - Hot Spot/'

# Load libraries
library(geosphere)
library(dplyr)
library(ggplot2)
library(lubridate)
library(kableExtra)
```

# Input track and other points of interest
```{r}
# define locations and track lines  21.317604, -157.967737
track1 <- data.frame(Lon=c(202.0323, 220, 220, 204, 202.0323)-360, Lat=c(21.3176, 30, 10, 19, 21.3176))
track2 <- data.frame(Lon=c(202.0323, 210, 210, 204, 202.0323)-360, Lat=c(21.3176, 30, 10, 19, 21.3176))
track3 <- data.frame(Lon=c(202.0323, 210, 210, 202.0323)-360, Lat=c(21.3176, 30, 10, 21.3176))

# Adding ARGO float drop locations
#argo <- data.frame(lon=c(-154,-151,-149,-147,-148,-148), lat=c(23.4,25,26,27,28.3,19))

```

# Pre-set which track, ship speed, etc
Change the parameters here for a different:

 - track
 
 - ship speed on each leg
 
 - start date
```{r}
track <- track3
speed1 <- 8.5
speed2 <- 8.5
speed3 <- 9
startDate <- as.POSIXct('2022-06-19 18:00')
sampTime_am <- 8
sampTime_pm <- 20
baseStn <- 5
extStn <- 23
argoStn <- 1
```

# Calculate time and distance for different station scenarios
```{r}
# Distances to 10N
distsM10 <- distGeo(track)[1:4]
```

# Parameters
The below is for a Start date of `r startDate`, with sampling starting at `r sampTime_am` and `r sampTime_pm` hours each day. 

Ship speed is: 

1) `r speed1` knots heading NE

2) `r speed2` knots heading S

3) `r speed3` knots heading NW

# Leg 1
This is the outbound leg leaving Pearl Harbor heading northeast to 30N and around 140W. This leg is mostly inside the gyre so we are only doing one extended station on this leg that will serve as our 'in gyre' or 'control' station. 

## Calculate timing and waypoints
Since there is only one station this bit is straight forward. I have added the ARGO deployment sites here since those require at least a slow down of the ships cruising speed to deploy the floats. 
```{r}
# Calculate bearing of track line
leg1_bearing <- bearing(track[1,], track[2,])

# Calculate where the halfway point is located along the track based on bearing
idx <- distsM10[1]*seq(0,1, by=1/5)
#idx[4] <- idx[4]+77868 # this is to move the 'middle' station forward so the timing getting there is better
leg1_qtr <- destPoint(track[1,], leg1_bearing, idx)

# Make data frame with starting and waypoint locations starting date, and sampling duration.
leg1_wpts <- data.frame(lon=leg1_qtr[,1], 
                        lat=leg1_qtr[,2], 
                        samp_hour=c(NA,NA,NA, NA, NA, NA), 
                        samp_dur=c(0, argoStn, argoStn, argoStn, argoStn, extStn), 
                        dist_to_here_NM=c(0, NA, NA, NA, NA, NA),
                        dateA=c(startDate, NA, NA, NA, NA, NA),
                        dateS=c(startDate, NA, NA, NA, NA, NA),
                        dateD=c(startDate, NA, NA, NA, NA, NA))
rownames(leg1_wpts) <- NULL
#leg1_wpts <- leg1_wpts[c(1,7),]  # this removes ARGO sites until I know where they should be

# Loop through each waypoint and calculate distance to that point, arrival date, sampling start date, and departure date for each station. 
for (i in 1:(nrow(leg1_wpts)-1)) {
  # Distance to next sampling site
  leg1_wpts$dist_to_here_NM[i+1] <- round(distGeo(leg1_wpts[i, 1:2], leg1_wpts[(i+1),1:2])/1852)
  # Date
  da2 <- (leg1_wpts$dist_to_here_NM[i+1]/speed1*60*60) + leg1_wpts$dateD[i]
  # Date and time of arrival at station
  leg1_wpts$dateA[i+1] <- da2
  # Date and time when sampling starts 
  if (leg1_wpts$samp_dur[i+1] < 20) {
    leg1_wpts$dateS[i+1] <- leg1_wpts$dateA[i+1]
  } else {
    leg1_wpts$dateS[i+1] <- ymd_h(ifelse(da2 <= ymd_h(paste0('2022-',month(da2), '-', day(da2), ' ', sampTime_am), tz = 'HST'), paste0('2022-',month(da2), '-', day(da2), ' ', sampTime_am), 
                                       ifelse(da2 > ymd_h(paste0('2022-',month(da2), '-', day(da2), ' ', sampTime_pm), tz = 'HST'), paste0('2022-',month(da2), '-', day(da2)+1, ' ', sampTime_am), paste0('2022-',month(da2), '-', day(da2), ' ', sampTime_pm))), tz='HST')
  }
  
  # Date and time when we are estimated to depart from the station
  leg1_wpts$dateD[i+1] <- leg1_wpts$dateS[i+1]+(leg1_wpts$samp_dur[i+1]*60*60)
  #leg1_wpts$dateD[i+1] <- ymd_h(ifelse(leg1_wpts$dateS[i+1] <= ymd_h(paste0('2022-',month(leg1_wpts$dateS[i+1]), '-', day(leg1_wpts$dateS[i+1]), ' ', sampTime_am),tz = 'HST'), paste0('2022-',month(leg1_wpts$dateS[i+1]), '-', day(leg1_wpts$dateS[i+1]), ' ', sampTime_am), paste0('2022-',month(leg1_wpts$dateS[i+1]), '-', day(leg1_wpts$dateS[i+1]), ' ', sampTime_pm)), tz='HST') + (leg1_wpts$samp_dur[i+1]*60*60)
  # Hour sampling is scheduled to start
  leg1_wpts$samp_hour[i+1] <- hour(leg1_wpts$dateD[i+1] - (leg1_wpts$samp_dur[i+1]*60*60))
}
```

## Check the output
```{r}
leg1_wpts %>%
  kbl() %>%
  kable_minimal()
```
# Leg 2
Leg 2 is following a meridian from north to south and stations are spaced every degree with extended stations every five degrees.
```{r eval=FALSE, include=FALSE}
# Number of way points along the trackline
n_pts <- 18 #21

# Sampling duration at each station
dur <- c(rep(c(extStn,rep(baseStn,3)),4),extStn) #c(rep(c(22, rep(5,4)),4),22)
#dur <- dur[-7]

# Make data frame with starting and waypoint locations starting date, and sampling duration.
leg2_wpts <- leg1_wpts[nrow(leg1_wpts),]

# Loop through way points to calculate date and time, distance, and sampling hours
for (i in 1:(n_pts-2)) {
  yesterday <- leg2_wpts[i,1:2]
  smpl_dur_ystrd <- leg2_wpts$samp_dur[i]
  smpl_dur_today <- dur[i+1]
  
  today <- yesterday
  if (i == 50) {
    today$lat <- today$lat-2
    dist_ystrd_today <- 120 # since stations are one degree apart, this is hardcoded
  } else {
    today$lat <- today$lat-1.25
    dist_ystrd_today <- 75 # since stations are one degree apart, this is hardcoded
}
  
  
  
  # Date and time of arrival on station
  dat <- leg2_wpts$dateD[i]+((dist_ystrd_today/speed2)*60*60)
  # Date and time of sample start
  dateA_today <- ymd_h(ifelse(dat <= ymd_h(paste0('2022-',month(dat), '-', day(dat), ' ', sampTime_am),tz = 'HST'), paste0('2022-',month(dat), '-', day(dat), ' ', sampTime_am), 
               ifelse(dat > ymd_h(paste0('2022-',month(dat), '-', day(dat), ' ', sampTime_pm),tz = 'HST'), paste0('2022-',month(dat), '-', day(dat)+1, ' ', sampTime_am), paste0('2022-',month(dat), '-', day(dat), ' ', sampTime_pm))), tz='HST')
  # Date and time sampling fihishes up/departing station
  dateD_today <- dateA_today+smpl_dur_today*60*60

  leg2_wpts <- rbind(leg2_wpts, data.frame(today, samp_hour=hour(dateA_today), samp_dur=smpl_dur_today, dist_to_here_NM=dist_ystrd_today, dateA=dat, dateS=dateA_today, dateD=dateD_today))
  rownames(leg2_wpts) <- c()
}
```

## Check the data
```{r eval=FALSE, include=FALSE}
leg2_wpts %>%
  kbl() %>%
  kable_minimal()
```
# Leg 2 alternative
This code calculates waypoints based on time between stations rather than fixed locations. 

```{r}
# LEG 2 Lat and lon of each waypoint along track (sampling 8am and 8pm)
leg2_bearing <- bearing(track[2,], track[3,])
leg2_qtr <- destPoint(track[2,], leg2_bearing, (distsM10[2]*c(0.25,0.50,0.75,1)))
leg2_wpts <- leg1_wpts[nrow(leg1_wpts),]

for (i in 1:25) {   #c(10,12:20)
  print(i)
  yesterday <- leg2_wpts[i,1:2]
  smpl_dur_ystrd <- leg2_wpts$samp_dur[i]
  steam_to_here <- ifelse(12-smpl_dur_ystrd < 0, 12-smpl_dur_ystrd+24, 12-smpl_dur_ystrd)
  #steam_to_here <- 5.25

  today <- destPoint(yesterday, leg2_bearing, d=(steam_to_here*speed2*1852))
  
  dist_ystrd_today <- distGeo(p1=yesterday, p2=today)/1852
  #smpl_dur_today <- 0
  
  if (distGeo(p1=today, p2=leg2_qtr[1,]) < 50000 ) {
    print('At one quarter point')
    smpl_dur_today <- extStn 
    #flag <- 2
  } else if (distGeo(p1=today, p2=leg2_qtr[2,]) < 60000 ) {
    print('At halfway point')
    smpl_dur_today <- extStn 
  } else if (distGeo(p1=today, p2=leg2_qtr[3,]) < 60000 ) {
    print('At three quarter point')
    smpl_dur_today <-extStn 
  } else if (distGeo(p1=today, p2=leg2_qtr[4,]) < 60000 ) {
    print('At end point')
    smpl_dur_today <-extStn 
  } else {
    smpl_dur_today <- baseStn
  }
 
  dateA_today <- leg2_wpts$dateD[i]+(steam_to_here*60*60)
  dateD_today <- dateA_today+(smpl_dur_today*60*60)
  
  leg2_wpts <- rbind(leg2_wpts, data.frame(today, samp_hour=hour(dateA_today), samp_dur=smpl_dur_today, dist_to_here_NM=dist_ystrd_today, dateA=dateA_today, dateS=dateA_today, dateD=dateD_today))
  
  if (today[2] < 10) { break }
}


if (leg2_wpts[nrow(leg2_wpts), 2] < 9.5) {
  leg2_wpts <- leg2_wpts[-nrow(leg2_wpts),]
}
```

## Check the data
```{r}
leg2_wpts %>%
  kbl() %>%
  kable_minimal()
```





# Leg 3
Leg 3 spans from 10N to Pearl Harbor. I had to dogleg the track around Big Island so tried to account for that in the timing. We are doing one station here, trying to match the longitude of the station on leg 1. If time allows, we'll add in another extended station about 1/4 way into the transect to capture the gradient of the edge of the gyre. 

I ended up doing the calculations on the way back manually. There is probably a more elegant way of doing it with looping.
```{r}
# Calculate the bearing
leg3_bearing <- bearing(track[3,], track[4,])

# Calculate where the halfway point is located along the track based on bearing
#leg3_qtr <- destPoint(track[3,], leg3_bearing, ((distsM10[3]+distsM10[4])*seq(0,1,by=0.005)))[c(50,100),]
#leg3_qtr <- destPoint(track[3,], leg3_bearing, (round(idx[7]-idx[4])+110750))
leg3_qtr <- destPoint(track[3,], leg3_bearing, c(speed3*c(13.3, 39)*60*60))

# Make data frame with starting and waypoint locations starting date, and sampling duration.
leg3_wpts <- leg2_wpts[nrow(leg2_wpts),]
leg3_wpts$lat <- round(leg3_wpts$lat)
#leg3_qtr2 <- destPoint(track[3,], leg3_bearing, (distGeo(track[3,], leg3_qtr)/2))

# leg3_wpts <-  rbind(leg3_wpts, data.frame(lon=c(leg3_qtr[1,1], leg3_qtr[2,1], track[4,1]),
#                          lat=c(leg3_qtr[1,2], leg3_qtr[2,2], track[4,2]),
#                          samp_hour=c(NA, NA, NA),
#                          samp_dur=c(extStn, extStn, 0),
#                          dist_to_here_NM=c(NA, NA, NA),
#                          dateA=c(NA, NA, NA),
#                          dateS=c(NA, NA, NA),
#                          dateD=c(NA, NA, NA)))
leg3_wpts <-  rbind(leg3_wpts, NA)
leg3_wpts[2,1:2] <- track[4,1:2]

rownames(leg3_wpts) <- NULL
#leg3_wpts <- leg3_wpts[c(1,4:5),]  

# # Calculate the distance to the first sampling location
# leg3_wpts$dist_to_here_NM[2] <- round(distGeo(leg3_wpts[1,1:2], leg3_wpts[2,1:2])/1852)
# da4 <- (leg3_wpts$dist_to_here_NM[2]/speed3*60*60) + leg3_wpts$dateD[1]
# leg3_wpts$dateA[2] <- da4
# leg3_wpts$dateS[2] <- ymd_h(ifelse(da4 <= ymd_h(paste0('2022-',month(da4), '-', day(da4), ' ', sampTime_am),tz = 'HST'), paste0('2022-',month(da4), '-', day(da4), ' ', sampTime_am),
#                                    ifelse(da4 > ymd_h(paste0('2022-',month(da4), '-', day(da4), ' ', sampTime_pm),tz = 'HST'), paste0('2022-',month(da4), '-', day(da4)+1, ' ', sampTime_am), paste0('2022-',month(da4), '-', day(da4), ' ', sampTime_pm))), tz='HST')
# leg3_wpts$dateD[2] <- ymd_h(ifelse(leg3_wpts$dateS[2] <= ymd_h(paste0('2022-',month(leg3_wpts$dateS[2]), '-', day(leg3_wpts$dateS[2]), ' ', sampTime_am),tz = 'HST'), paste0('2022-',month(leg3_wpts$dateS[2]), '-', day(leg3_wpts$dateS[2]), ' ', sampTime_am), paste0('2022-',month(leg3_wpts$dateS[2]), '-', day(leg3_wpts$dateS[2]), ' ', sampTime_pm)), tz='HST') + (leg3_wpts$samp_dur[2]*60*60)
# leg3_wpts$samp_hour[2] <- hour(leg3_wpts$dateD[2] - (leg3_wpts$samp_dur[2]*60*60))
# 
# # Calculate the distance to the second sampling location
# leg3_wpts$dist_to_here_NM[3] <- round(distGeo(leg3_wpts[2,1:2], leg3_wpts[3,1:2])/1852)
# da4 <- (leg3_wpts$dist_to_here_NM[3]/speed3*60*60) + leg3_wpts$dateD[2]
# leg3_wpts$dateA[3] <- da4
# leg3_wpts$dateS[3] <- ymd_h(ifelse(da4 <= ymd_h(paste0('2022-',month(da4), '-', day(da4), ' ', sampTime_am),tz = 'HST'), paste0('2022-',month(da4), '-', day(da4), ' ', sampTime_am),
#                                    ifelse(da4 > ymd_h(paste0('2022-',month(da4), '-', day(da4), ' ', sampTime_pm),tz = 'HST'), paste0('2022-',month(da4), '-', day(da4)+1, ' ', sampTime_am), paste0('2022-',month(da4), '-', day(da4), ' ', sampTime_pm))), tz='HST')
# leg3_wpts$dateD[3] <- ymd_h(ifelse(leg3_wpts$dateS[3] <= ymd_h(paste0('2022-',month(leg3_wpts$dateS[3]), '-', day(leg3_wpts$dateS[3]), ' ', sampTime_am),tz = 'HST'), paste0('2022-',month(leg3_wpts$dateS[3]), '-', day(leg3_wpts$dateS[3]), ' ', sampTime_am), paste0('2022-',month(leg3_wpts$dateS[3]), '-', day(leg3_wpts$dateS[3]), ' ', sampTime_pm)), tz='HST') + (leg3_wpts$samp_dur[3]*60*60)
# leg3_wpts$samp_hour[3] <- hour(leg3_wpts$dateD[3] - (leg3_wpts$samp_dur[3]*60*60))
# 
# # Calculate the timing and distance to the dogleg at big island
# leg3_wpts$dist_to_here_NM[2] <- round(distGeo(leg3_wpts[2,1:2], leg3_wpts[1,1:2])/1852)
# leg3_wpts$dateS[2] <- (leg3_wpts$dist_to_here_NM[2]/speed3*60*60) + leg3_wpts$dateD[1]
# leg3_wpts$dateD[2] <- leg3_wpts$dateS[2] + (leg3_wpts$samp_dur[2]*60*60)
# leg3_wpts$dateA[2] <- leg3_wpts$dateS[2]

# And timing and distance to Pearl Harbor
leg3_wpts$dist_to_here_NM[2] <- round(distGeo(leg3_wpts[1,1:2], leg3_wpts[2,1:2])/1852)
leg3_wpts$dateS[2] <- (leg3_wpts$dist_to_here_NM[2]/speed3*60*60) + leg3_wpts$dateD[1]
leg3_wpts$dateA[2] <- leg3_wpts$dateS[2]
```

## Check the data
```{r}
leg3_wpts %>%
  kbl() %>%
  kable_minimal()
```
# Put it all together and plot
## All way points
```{r}
# Bind the way points from all three legs together
all_wpts <- rbind(leg1_wpts, leg2_wpts[-1,], leg3_wpts[-1,])
rownames(all_wpts) <- NULL
# Add station descriptions
all_wpts$stn_type <- ifelse(all_wpts$samp_dur > 10, 'extended', ifelse(all_wpts$samp_dur == 5, 'base', ifelse(all_wpts$samp_dur == 1, 'argo','none')))
all_wpts$stn <- ''
# Label the extended stations
all_wpts$stn[which(all_wpts$stn_type == 'extended')] <- LETTERS[1:5]
# Change some labels to more intutiive ones
all_wpts <- all_wpts %>% 
  rename('datetime_arrival'=dateA, 'datetime_samp_start'=dateS, 'datetime_departure'=dateD) %>% 
  mutate(lon=round(lon, 2), lat=round(lat, 2))
# Calculate time 'wasted' between arrival at station and sampling starting
all_wpts$time_btwn_arrival_samp = all_wpts$datetime_samp_start-all_wpts$datetime_arrival
units(all_wpts$time_btwn_arrival_samp) <- 'hours'
all_wpts$time_btwn_arrival_samp <- round(all_wpts$time_btwn_arrival_samp, 1)
```

```{r}
kbl(all_wpts) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```


## Make a plot
```{r, fig.height=8, fig.cap="SE2204 trackline. Arrows denote direction, blue symbols are extended stations and yellow symbols are base stations. Circles are daytime sampling stations and squares are nighttime sampling staions. Red diamonds are proposed ARGO deployment sites."}
argo2 <- all_wpts %>% 
    filter(stn_type == 'argo'| stn == 'A' | stn == 'C') #%>% full_join(argo[6,])

if (track$Lon[2] == -140) {
  plt1 <- ggplot() +
  borders("world",
          xlim = c(-160, -140),
          ylim = c(18, 25),
          fill="gray",colour="grey40", size=0.25) +
  coord_map() +
  geom_path(data=all_wpts, aes(lon, lat)) +
  geom_point(data=all_wpts[which(all_wpts$stn_type == 'base'),], aes(lon, lat, shape=factor(samp_hour)), color='#E69f00', size=2.5) + 
  geom_point(data=all_wpts[which(all_wpts$stn_type == 'extended'),], aes(lon, lat, shape=factor(samp_hour)), color='#56B4E9', size=4) +
  scale_shape_manual(values=c('8' = 19, '20'= 15)) + 
  #geom_point(data=argo, aes(lon, lat), shape=18, color='green', size=3, alpha=0.75) +
  #geom_point(data=argo2, aes(lon, lat), shape=18, color='firebrick', size=3, alpha=0.75) +
  geom_text(data=all_wpts[which(all_wpts$stn_type == 'extended'),], aes(lon, lat, label=stn), hjust = 0, nudge_x = 0.75) +
  geom_segment(lineend = "round", linejoin = "bevel", size=0.5, aes(x = c(-155, -138, -145), y = c(25, 27, 11), xend = c(-145, -138, -155), yend = c(29.5, 13, 16.5)), color='gray', arrow = arrow(length = unit(0.25, "cm"))) +
  theme_bw() +
  theme(legend.position = "none") +
  xlab('Longitude') +
  ylab('Latitude') +
  xlim(c(-160,-137)) +
  ylim(c(8,32))
} else {
  plt1 <- ggplot() +
  borders("world", 
          xlim = c(-160, -140), 
          ylim = c(18, 25),
          fill="gray",colour="grey40", size=0.25) +
  coord_map() +
  geom_path(data=all_wpts, aes(lon, lat)) +
  geom_point(data=all_wpts[which(all_wpts$stn_type == 'base'),], aes(lon, lat, shape=factor(samp_hour)), color='#E69f00', size=2.5) + 
  geom_point(data=all_wpts[which(all_wpts$stn_type == 'extended'),], aes(lon, lat, shape=factor(samp_hour)), color='#56B4E9', size=4) +
  geom_point(data=argo2, aes(lon, lat), shape=18, color='firebrick', size=3, alpha=0.75) +
  scale_shape_manual(values=c('8' = 19, '20'= 15)) + 
  geom_text(data=all_wpts[which(all_wpts$stn_type == 'extended'),], aes(lon, lat, label=stn), hjust = 0, nudge_x = 0.75) +
  geom_text(data=all_wpts[which(all_wpts$stn %in% c('A', 'E')),], aes(lon, lat, label=format(datetime_samp_start, '%d %b %Y')), nudge_y = c(1,-1), fontface = "italic") +
  geom_segment(lineend = "round", linejoin = "bevel", size=0.5, aes(x = c(-157, -148, -153), y = c(23.7, 27, 13), xend = c(-153, -148, -157), yend = c(28, 13, 18.5)), color='gray', arrow = arrow(length = unit(0.25, "cm"))) +
  #geom_segment(lineend = "round", linejoin = "bevel", size=0.5, aes(x = c(-155, -143, -148), y = c(25, 27, 10.5), xend = c(-150, -143, -155), yend = c(28.5, 13, 16.5)), color='gray', arrow = arrow(length = unit(0.25, "cm"))) +
  theme_bw() +
  theme(legend.position = "none") +
  xlab('Longitude') +
  ylab('Latitude') +
  xlim(c(-160,-137)) +
  ylim(c(8,32)) + 
  ggtitle(paste('Depart', format(startDate, '%d %b %Y %H:%M')), subtitle=paste('NS transect speed', speed2, 'knots'))
}
plt1
```


# Save the data
```{r}
#Set file names
tblName <- paste0('SE2204_wpt_timing_', abs(track$Lon[2]), '_19JUN.csv')
pltName <-paste0('SE2204_track_wpt_timing_', abs(track$Lon[2]), '_19JUN.png')

# Save the way points
write.csv(all_wpts, tblName, row.names=F)
  
# save the map
ggsave(filename=pltName, plot=plt1, width=5, height=6, dpi=200, units='in')



```

```{r eval=FALSE, include=FALSE}
library(marmap)

hiBathy <- getNOAA.bathy(-160,-135,8,32)

blues <- c("lightsteelblue4", "lightsteelblue3",
           "lightsteelblue2", "lightsteelblue1")
greys <- c(grey(0.6), grey(0.93), grey(0.99))

plot(hiBathy, image=T, land = T, lwd=0.03, bpal=list(c(0, max(hiBathy), greys),
                                                     c(min(hiBathy), 0, blues)))
#plot(hiBathy, n = 1, lwd = 0.4, add = TRUE)
lines(all_wpts)
points(all_wpts[which(all_wpts$stn_type == 'base'),1:2], pch=21, col='black', bg='#E69f00')
points(all_wpts[which(all_wpts$stn_type == 'extended'),1:2], pch=21, col='black', bg='#56B4E9', cex=1.2)
text(all_wpts[which(all_wpts$stn_type == 'extended'),1]+1, all_wpts[which(all_wpts$stn_type == 'extended'),2], LETTERS[1:8])
```

```{r eval=FALSE, include=FALSE}
autoplot(hiBathy, geom = c("raster")) + 
    scale_fill_gradientn(values = scales::rescale(c(-6600, 0, 1, 3820)),
                         colors = c("steelblue4", "#C7E0FF", "grey50", "grey80")) +
  geom_path(data=all_wpts, aes(lon, lat)) +
  geom_point(data=all_wpts[which(all_wpts$stn_type == 'base'),], aes(lon, lat, shape=factor(samp_hour)), color='#E69f00', size=2.5) + 
  geom_point(data=all_wpts[which(all_wpts$stn_type == 'extended'),], aes(lon, lat, shape=factor(samp_hour)), color='#56B4E9', size=4) +
  scale_shape_manual(values=c('8' = 19, '20'= 15)) + 
  #geom_point(data=argo2, aes(lon, lat), shape=18, color='firebrick', size=3, alpha=0.75) +
  geom_text(data=all_wpts[which(all_wpts$stn_type == 'extended'),], aes(lon, lat, label=stn), hjust = 0, nudge_x = 0.75) +
  #geom_segment(lineend = "round", linejoin = "bevel", size=0.5, aes(x = c(-155, -143, -148), y = c(25, 27, 10.5), xend = c(-150, -143, -155), yend = c(28.5, 13, 16.5)), color='gray', arrow = arrow(length = unit(0.25, "cm"))) +
  theme_bw() +
  theme(legend.position = "none") +
  xlab('Longitude') +
  ylab('Latitude')
```


